### 2015-05-14 background.tex
lockset figure hack
hacks in bg

Lockset analysis is a lightweight race detection method proposed in the context of Eraser~\cite{savage1997eraser}, a dynamic data race detector.  The idea is to track the set of locks that are \emph{consistently} used to protect a memory location during program execution. If that lockset ever becomes empty, the analysis reports a potential race on that memory location. This is because an inconsistent lockset suggests that a memory location \emph{may} be accessed simultaneously by two or more threads.

@@

Figure~\ref{fig:locksets} shows an example of applying lockset analysis on a concurrent program consisting of two threads $T_1$ and $T_2$, both accessing a global variable $A$. Initially, $\mathit{LS}_A$, which is the lockset for A, contains all possible locks in the program: $M$ and $N$. During execution of $T_1$, the thread writes $A$ without holding $N$, and thus $N$ is removed from $\mathit{LS}_A$. Next, during execution of $T_2$, the thread writes $A$ without holding $M$, and thus $\mathit{LS}_A$ becomes empty. Finally, a warning is reported because the two threads do not consistently protect $A$.

>>>>

Lockset analysis is a lightweight race detection method proposed in the context of Eraser~\cite{savage1997eraser}, a dynamic data race detector.  The idea is to track the set of locks that are \emph{consistently} used to protect a memory location during program execution. If that lockset ever becomes empty, the analysis reports a \emph{potential} race on that memory location. This is because an inconsistent lockset suggests that a memory location \emph{may} be accessed simultaneously by two or more threads.

@@

Figure~\ref{fig:locksets} shows an example of applying lockset analysis on a concurrent program consisting of two threads $T_1$ and $T_2$, both accessing a global variable $A$. Initially, $\mathit{LS}_A$, which is the lockset for A, contains all possible locks in the program: $M$ and $N$. During execution of $T_1$, the thread writes $A$ without holding $N$, and thus $N$ is removed from $\mathit{LS}_A$. Next, during execution of $T_2$, the thread writes $A$ without holding $M$, and thus $\mathit{LS}_A$ becomes empty. As a result, a warning is reported because the two threads do not consistently protect $A$.
